Stat 495 - Logistic Regression Practice - CS Game

### 2022-09-07 labs/CSGameLogRegression.Rmd
Added some files

```{r, include = FALSE}
library(mosaic)
library(readr)
library(broom)
```

@@

>>>>

```{r, include = FALSE}
library(mosaic)
library(readr)
library(broom)
library(mosaic)
library(Stat2Data)
library(lmtest)
library("DescTools")
```

@@

```{r}
glimpse(csgame)
```

```{r}
ggplot(csgame, aes(x = as.factor(OutcomeNum), y = BaseAttack)) + geom_boxplot() + labs(x = "Outcome Num")
ggplot(csgame, aes(x = as.factor(OutcomeNum), y = Charisma)) + geom_boxplot() + labs(x = "Outcome Num")
ggplot(csgame, aes(x = as.factor(OutcomeNum), y = MonsterMagic)) + geom_boxplot() + labs(x = "Outcome Num")
ggplot(csgame, aes(x = as.factor(OutcomeNum), y = Dexterity)) + geom_boxplot() + labs(x = "Outcome Num")
ggplot(csgame, aes(x = as.factor(OutcomeNum), y = Intelligence)) + geom_boxplot() + labs(x = "Outcome Num")
ggplot(csgame, aes(x = as.factor(OutcomeNum), y = Constitution)) + geom_boxplot() + labs(x = "Outcome Num")
ggplot(csgame, aes(x = as.factor(OutcomeNum), y = MonsterAttack)) + geom_boxplot() + labs(x = "Outcome Num")
ggplot(csgame, aes(x = as.factor(OutcomeNum), y = BaseDefense)) + geom_boxplot() + labs(x = "Outcome Num")
ggplot(csgame, aes(x = as.factor(OutcomeNum), y = ZoneLevel)) + geom_boxplot() + labs(x = "Outcome Num")
ggplot(csgame, aes(x = as.factor(OutcomeNum), y = MagicDefense)) + geom_boxplot() + labs(x = "Outcome Num")
```

```{r}
# Add log Price
csgame <- mutate(csgame, logBaseDefense = log(BaseDefense))
csgame <- mutate(csgame, logMagicDefense = log(MagicDefense))
#Fit model and get basic output
logm <- glm(OutcomeNum ~ logBaseDefense + logMagicDefense,
            data = csgame, family = binomial(logit))
msummary(logm)
```

```{r}
lrtest(logm)
```
```{r}
exp(confint(logm))
```
```{r}
logmaugment <- logm %>% augment(type.predict = "response")
names(logmaugment)
```

```{r}
logmaugment <- mutate(logmaugment, binprediction = round(.fitted, 0))
tally(~ binprediction, data = logmaugment)

tally(~ OutcomeNum, data = csgame)
```
